Effect of Beam Chromaticity on Foregrounds in Wide-Field Measurements of Redshifted 21~cm Power Spectra

### 2016-03-03 ForegroundSimulations/ms.tex
Comment some lines in EoR sensitivity section
From e4fc215 (restructure):
==========================

In ms.tex,

(*) Comment some lines in EoR sensitivity section

Firstly, it is noted that the coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}. Secondly, it is also found that barring the shortest baselines ($|\boldsymbol{b}| \leq $~29.2~m), which have the most severe foreground contamination especially from diffuse emission, foreground contamination on baselines longer than $\gtrsim 29.2$~m is lesser than EoR signal power for $|k_\parallel| \gtrsim 0.22\,h$~Mpc$^{-1}$ in either of the models.

Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} is similar to Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} except it is obtained with a subband {\it Blackman-Harris} window function centered on 170~MHz. In this subband relative to that centered on 150~MHz, the ratio of powers of the EoR signal and foregrounds is even higher outside the wedge thus indicating a stronger potential for direct detectability without the use of optimal power spectrum estimation techniques on almost all baseline lengths.

% \begin{figure*}[htb]
% \centering
% \includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}
% \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
% \label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
% \end{figure*}

It must be emphasized that these are obtained only with windowing techniques and do not represent the best sensitivity achievable with sophisticated tools such as optimal covariance-based weighting schemes \citep{liu14a,liu14b,ali15,dil15}. Thus assuming the data is limited by foregrounds and not by thermal noise, this demonstrates that even with no sophistication in power spectrum estimation, a direct detection based on simple windowing and delay spectrum technique is possible on a majority of HERA baselines and will further allow distinguishing between different EoR models. This finding holds even in the most conservative scenario where the modeled beam pattern with most severe chromaticity inherently results in significant and inherent foreground contamination outside the {\it foreground wedge}.

>>>>

% Firstly, it is noted that the coarsening of delay resolution significantly absorbs the distinct differences caused by beams of different chromaticities as seen in the full band foreground delay spectra outside the {\it foreground wedge} in Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines}. Secondly, it is also found that barring the shortest baselines ($|\boldsymbol{b}| \leq $~29.2~m), which have the most severe foreground contamination especially from diffuse emission, foreground contamination on baselines longer than $\gtrsim 29.2$~m is lesser than EoR signal power for $|k_\parallel| \gtrsim 0.22\,h$~Mpc$^{-1}$ in either of the models.

% Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-170-subband} is similar to Fig.~\ref{fig:asm-dps-beam-chromaticity-baselines-150-subband} except it is obtained with a subband {\it Blackman-Harris} window function centered on 170~MHz. In this subband relative to that centered on 150~MHz, the ratio of powers of the EoR signal and foregrounds is even higher outside the wedge thus indicating a stronger potential for direct detectability without the use of optimal power spectrum estimation techniques on almost all baseline lengths.

% % \begin{figure*}[htb]
% % \centering
% % \includegraphics[width=\linewidth]{sim_asm_foreground_eor_beam_chromaticity_170.0_MHz_subband_win_method_bhw2.0.eps}
% % \caption{Effect of chromaticity of antenna power pattern on foreground delay power spectra obtained from the 170~MHz subband for different baseline lengths.}
% % \label{fig:asm-dps-beam-chromaticity-baselines-170-subband}
% % \end{figure*}

% It must be emphasized that these are obtained only with windowing techniques and do not represent the best sensitivity achievable with sophisticated tools such as optimal covariance-based weighting schemes \citep{liu14a,liu14b,ali15,dil15}. Thus assuming the data is limited by foregrounds and not by thermal noise, this demonstrates that even with no sophistication in power spectrum estimation, a direct detection based on simple windowing and delay spectrum technique is possible on a majority of HERA baselines and will further allow distinguishing between different EoR models. This finding holds even in the most conservative scenario where the modeled beam pattern with most severe chromaticity inherently results in significant and inherent foreground contamination outside the {\it foreground wedge}.
